### 2019-08-10 conclusions.tex
General touching up

The expected limit on \mmed\ for the DM simplified models, based on prefit expected yields,
it 200\unit{GeV} higher than the observed limit. This is consistent with the excess of observed data at high \ETgamma\ compared to the prefit
expected yield (see Fig.~\ref{fig:postfitDM_SR}), and also consistent with the larger value of the expected limits on $\Lambda$ and \mD\ compared
to the observed limits (see Figs.~\ref{fig:DMEWKlimits}, \ref{fig:MDLimits}). A total of 16 observed events populate the highest \ETgamma\ bin
in both signal regions combined, and the statistical errors relating to this bin are a sizable fraction of the total event count, motivating the
conjecture that the large ratio of observed to predicted events is a statistical fluke. However, as noted in sec.~\ref{sec:results_znng_xsec}, the probability
of the \zinvg\ process alone contributing the number of observed events in the highest \ETgamma\ bin is rather small, assuming that the \zinvg\ cross
section is adequately modeled by the MATRIX NNLO predictions and that the behavior of \zinvg\ events in the CMS experiment is adequately modeled
by the MADGRAPH5+GEANT4 simulations. Either of these may in fact be insufficiently accurate at high \pTgamma, relative to current experimental
sensitivity. Alternatively, some unknown or inadequately modeled source of background may be making a significant contribution. The most
provocative possibility is that this represents the first subtle glimpse of BSM physics, though the estimated probability of a \zinvg\ fluctuation
is thousands of times higher than the accepted threshold to claim such a discovery. Some combination of any or all of these possibilities may be true.
Additional data would improve the statistical precision of the high-\ETgamma\ yield estimates, sharpening any potential excesses, or else
``regressing to the mean'' and leveling out to the current SM predictions.

>>>>

The expected limit on \mmed\ for the DM simplified models, based on prefit expected yields,
it 200\unit{GeV} higher than the observed limit. This is consistent with the excess of observed data at high \ETgamma\ compared to the prefit
expected yield (see Fig.~\ref{fig:postfitDM_SR}), and also consistent with the larger value of the expected limits on $\Lambda$ and \mD\ compared
to the observed limits (see Figs.~\ref{fig:DMEWKlimits}, \ref{fig:MDLimits}). A total of 16 observed events populate the highest \ETgamma\ bin
in both signal regions combined, and the statistical errors relating to this bin are a sizable fraction of the total event count, motivating the
conjecture that the large ratio of observed to predicted events is a statistical fluke. However, as noted in sec.~\ref{sec:results_znng_xsec}, the probability
of the \zinvg\ process alone contributing the number of observed events in the highest \ETgamma\ bin is rather small, assuming that the \zinvg\ cross
section is adequately modeled by the MATRIX NNLO predictions and that the behavior of \zinvg\ events in the CMS experiment is adequately modeled
by the MadGraph5+GEANT4 simulations. Either of these may in fact be insufficiently accurate at high \pTgamma, relative to current experimental
sensitivity. Alternatively, some unknown or inadequately modeled source of background may be making a significant contribution. The most
provocative possibility is that this represents the first subtle glimpse of BSM physics, though the estimated probability of a \zinvg\ fluctuation
is thousands of times higher than the accepted threshold to claim such a discovery. Some combination of any or all of these possibilities may be true.
Additional data would improve the statistical precision of the high-\ETgamma\ yield estimates, sharpening any potential excesses, or else
``regressing to the mean'' and leveling out to the current SM predictions.

### 2019-08-10 estimation.tex
General touching up

\chapter{Signal and background estimation} \label{chap:background_estimation}
\section{Yields from simulation} \label{sec:background_estimation_simulated}
If a well-validated MC sample exists for a given process (Ch.~\ref{chap:simulation}), and if appropriate data--MC correction factors are applied (Ch.~\ref{chap:event_selection}),
the expected event yield contributed by that process to a given signal or control region may be estimated entirely within simulation.
After generating some large number of events (sufficient to render statistical uncertainties negligible with respect to other sources of uncertainty),
running them through the detector simulation, and reconstructing the results, the appropriate signal or control region cuts are finally applied to the simulated events.
The number of events passing all cuts, divided by the total number of events generated, gives a maximum-likelihood (ML) estimate of the probability that
an event of the kind modeled by the sample will contribute to the final observed event tally. This probability is often written as the product of two factors: the
probability that an event lies within the kinematic coverage of the detector, and the probability that an event within the kinematic coverage passes selection cuts,
called the \textit{acceptance} ($A$) and \textit{efficiency} ($\epsilon$), respectively. The expected contribution of a given process to a final event tally is therefore given by
\begin{equation}
\mathrm{expected\ yield} = A*\epsilon*\sigma*L
\end{equation}
where $\sigma$ is the total cross section of a given process (having kinematic properties within the range modeled by the MC sample) and $L$ is the integrated
luminosity of the observed dataset (35.9\fbinv).

\section{Electron faking photon} \label{sec:background_estimation_elefake}
An inclusive estimate of the electron faking photon yield, summed over all processes with an isolated final-state electron, is obtained using a \textit{fake ratio} method.
The ratio of the numbers of successful vs. unsuccessful fakes is evaluated in a dedicated control region, designed in such a way that this ratio is expected to be equally
valid in the signal regions. Multiplying this ratio by the observed number of unsuccessful fake events in the signal regions gives an estimate of the number of successful
fake events in the signal regions. This last step in particular distinguishes the fake ratio method from e.g. finding a data--MC correction factor and applying that to
a purely MC-derived estimate of electron fake yields. Since the final expected yield is proportional to a set of observed (as opposed to simulated) data,
this is known as a \textit{data-driven} method.

@@

\section{Jet faking photon} \label{sec:background_estimation_jetfake}
Like the electron faking photon background, the expected jet faking photon background is estimated via a data-driven method employing a fake ratio.
The numerator of the fake ratio should be the number of fake photon events originating from jets (passing any given signal or control region definition), and so
is defined by selecting events with a leading photon passing our standard photon ID.
The denominator should the number of events in which a high-\ET\ reconstructed photon is surrounded by so much energy from other particles
that it fails a loose set of isolation criteria (and so the photon is likely a jet constituent rather than a true hard-process photon); it is defined by selecting events
with a photon failing a relatively loose ID that has a 90\% selection efficiency for real photons\footnote{Denominator events must still pass a
``very loose'' ID with five times higher maximum isolation cuts.}.

@@

\section{Spikes} \label{sec:background_estimation_spikes}
Due to their idiosyncratic means of production, spikes do not currently have simulated samples that could be expected to accurately reproduce their expected yield,
particularly in the case of events somehow passing all the spike cleaning cuts in the monophoton signal regions. Instead, the time distribution of clearly-identified
spikes in observed events can be used to extrapolate the preponderance of spikes within the in-time window ($|t|<3\unit{ns}$) defined by our signal region cuts.
This time distribution is examined by performing a custom reconstruction of the data in which ``spike-killer'' cuts that are part of standard event reconstruction
are omitted. Spike candidates are selected from reconstructed photons that pass a loosened set of ID criteria with no isolation cuts (to account for the different
characteristics of events outside the in-time window) but have $\ETgamma > 175\unit{GeV}$, $\sieie < 0.0104$, and either \sieie\ or $\sipip < 0.1$.
As illustrated in Fig.~\ref{fig:fulltime_templates}, this distribution exhibits a peak around $t = -15\unit{ns}$ and falls off to near zero by the in-time window.

@@

\begin{table}[tbp]
  \begin{center}
    \caption{
      The values of the response matrix $K$, estimated in \zinvg\ MadGraph MC with higher order corrections applied.
      With rows ordered from top to bottom and columns ordered from left to right, the value in row $i$, column $j$
      is equal to the conditional probability of a \zinvg\ event to pass all signal region cuts and land in reconstructed
      \ETgamma\ bin $j$, if its true \pTgamma\ value is in bin $i$.
    }
    \label{tab:response_matrix_values}
    \begin{tabular}{c c c c c c}
      \hline
       0.297401 & 0.0428149 & 0.000595967 & 5.87982e-05 & 0 & 0 \\
       0.0399934 & 0.38611 & 0.049973 & 0.000505446 & 0.000133614 & 0 \\
       0.000202488 & 0.0214437 & 0.37027 & 0.0326231 & 0.000264926 & 0.000183209 \\
       0 & 0.000196144 & 0.0229108 & 0.367465 & 0.0249473 & 0 \\
       0 & 0 & 1.50756e-05 & 0.0100609 & 0.343767 & 0.022748 \\
       0 & 0 & 0 & 0 & 0.00326465 & 0.316482 \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

Measuring the \zinvg\ differential cross section amounts to extracting the true number of \zinvg\ events in each bin of \pTgamma, and
dividing by the integrated luminosity of our dataset. We denote the total numbers of events expected in each of our six reconstructed
\ETgamma\ bins by a vector $N$, and the expected background (anything other than \zinvg) by a vector $b$. The numbers
of produced \zinvg\ events, represented by $\lambda$, are related to $N$ and $b$ by the expected response matrix $K$ according to
\begin{equation}
  N = K \lambda + b.
\end{equation}
The problem of extracting the differential \zinvg\ cross section from the observed \ETgamma\ distribution---unfolding---is then essentially a problem
of matrix inversion, in which we want to find
\begin{equation}
  \lambda = K^{-1} (N - b).
\end{equation}

@@

Because $K$ is strongly diagonal and has similar values all along its diagonal, its inversion is not expected to result in any mathematical pathologies.
The condition number of the matrix, defined to be the ratio of its largest to its smallest singular value, is 1.5363. It is invertible, and
its inversion produces positive estimates of the cross section in every \ETgamma\ bin. There is no clear motivation to employ any sort of regularization
strategy in the ML fit, and we do not employ any such strategy.

@@

\begin{table}
  \begin{center}
    \caption{NNLO / LO correction factors for \zinvg\ and \wlng\ samples.}
    \label{tab:zg_kfactors}
    \begin{tabular}{| l | r | r |}
      \hline
      \pTgamma\ [GeV] & \zinvg & \wlng \\
      \hline
      \hline
      $[175, 190]$ & 1.44 & 1.40 \\
      \hline
      $[190, 250]$ & 1.41 & 1.37 \\
      \hline
      $[250, 400]$ & 1.35 & 1.31 \\
      \hline
      $[400, 700]$ & 1.29 & 1.26 \\
      \hline
      $[700, \inf]$ & 1.15 & 1.15 \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

@@

The differential cross section after all higher-order corrections are applied may be written as
\begin{equation}
  d\sigma^{\mathrm{NNLO\ QCD}+\mathrm{NLO\ EWK}} = d\sigma^{\mathrm{LO}} k^{\mathrm{NNLO\ QCD}} (1 + \kappa^{\mathrm{EWK\ Sudakov}} + \kappa^{\mathrm{EWK\ \Pq\Pgamma}}),
\end{equation}
where $k^{\mathrm{NNLO\ QCD}} = d\sigma^{\mathrm{NNLO\ QCD}} / d\sigma^{\mathrm{LO}}$, and the two $\kappa$
terms are the Sudakov suppression and photon-induced enhancement components of the EWK
correction, respectively. Theoretical uncertainties on the EWK corrections are not currently well-understood. In this thesis,
the magnitudes of the uncertainties on $\kappa^{\mathrm{EWK\ Sudakov}}$ and $\kappa^{\mathrm{EWK\ \Pq\Pgamma}}$ are estimated
to be $(\kappa^{\mathrm{EWK\ Sudakov}})^2$ and $\kappa^{\mathrm{EWK\ \Pq\Pgamma}}$, i.e. the square of
the correction and 100\% of the correction, respectively\footnote{Choosing the square of $\kappa^{\mathrm{EWK\ Sudakov}}$ is motivated by the fact
that fully resummed leading-log Sudakov suppression is an exponential function of $\kappa^{\mathrm{EWK\ Sudakov}}$.}.

@@

\section{Signal estimation: SM} \label{sec:signal_extraction_SM}
Beam halo is the only process examined in this analysis with an anisotropic $\phi$ distribution.
Figure~\ref{fig:halophi} shows the distribution of beam halo photons as a function of $\phi'$.
To constrain the beam halo normalization, the signal region is split into two parts according to $|\phi'|$.
The parts defined by $|\phi'| < 0.5$ and $|\phi'| > 0.5$ are respectively called the horizontal ($H$) and vertical ($V$) signal
regions. All other sources of events have expected yields that are isotropic in $\phi$, and therefore
are expected to fall into the two signal regions in direct proportion to the $\phi$ coverage of those regions.
The fraction of the total $\phi$ span covered by signal region $S$ is denoted by $C_{S}$ ($S \in \{H,V\}$).

@@

Using the above definitions for $C_{S}$, $r_{i}$, $\nZg[j,i]$, $h$, and $\nhalo[,j]$,
the total reconstructed event yield \nS\ in each signal region is estimated according to
\begin{equation}
  \nS[,j] = C_{S} (\Sigma_{i}r_{i}\nZg[j,i] + \nWg[j] + b_{j}) + h\nhalo[,j],
\end{equation}
where $\nWg[j]$ is the total contribution of \wlng\ events to reco bin $j$, and $b_{j}$ is the total contribution to reco bin $j$ from
electron and hadron misidentification, ECAL spikes, and other minor SM background processes, in both signal regions combined.

The ratios (\textit{transfer factors}) of the bin-by-bin yields of \wlng\ in the signal regions to those
of \wlng\ in the single-lepton control regions are denoted by \RWl[,j]. These are estimated in MC.
The total reconstructed event yield \nl\ in each single-$\ell$ control region ($\ell \in \{e,\mu\}$) is estimated according to
\begin{equation}
  \nl[,j] = \frac{\nWg[j]}{\RWl[,j]} + b_{\ell\Pgamma,j},
\end{equation}
where \nWg\ is the number of \wlng\ events in the combined signal regions, and
$b_{\ell\Pgamma}$ is the predicted contribution from other background sources in the single-$l$ control region.
Figure~\ref{fig:tf_w} shows the transfer factors relating the \wlng\ yield in the single-lepton control regions to the \wlng\ yield in the
vertical signal region.

@@

The complete likelihood function that is maximized in the SM cross section fit is
\begin{align}
  \mathcal{L} & = \left\{ \mathcal{L_{\text{Signal}}} \mathcal{L_{\text{Control}}} \right\} \times \mathcal{L_{\text{Nuisances}}} \\
  & = \prod_{j} \left\{
    \prod_{S=H,V} \mathcal{P}\left( N_{S, j} \left| \nS[,j] (\vec{\theta} \right.) \right) \prod_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \nl[,j] (\vec{\theta}) \right. \right) 
    \right\}  \times \prod_{t} \mathcal{N}(\theta_t) \\
  & = \prod_{j} \left\{
  \begin{array}{cc}
    \prod\limits_{S=H,V} \mathcal{P}\left( N_{S, j} \left| C_{S} \left(\Sigma_{i}r_{i}\nZg[j,i](\vec{\theta}) + \nWg[j] + b_{j}(\vec{\theta})\right) + h \nhalo[,j](\vec{\theta}) \right. \right) \\[1.3pt]
    \times \prod\limits_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \frac{\nWg[j]}{\RWl[,j](\vec{\theta})} + b_{\ell\Pgamma, j}(\vec{\theta}) \right. \right) \\[1.3pt]
  \end{array} \right\}
  \times \prod_{t} \mathcal{N}(\theta_t),
\end{align}
following the notation introduced above, and where $\mathcal{P}(N\vert\lambda)$ is the Poisson probability of $N$ for mean $\lambda$,
$\mathcal{N}$ denotes the unit normal distribution centered at zero, and $N_{X,i}$ is the observed number of events in reco bin i of region X.

@@

The total reconstructed event yield \nS\ in each signal region is estimated according to
\begin{equation}
  \nS[,j] = C_{S} (\mu s_{j} + (1 + \fZW[,j])\nZg[j,all] + b_{j}) + h\nhalo[,j],
\end{equation}
where $\nZg[j,all]$ refers to the total contribution from all \zinvg\ events to reco \ETgamma\ bin $j$, $s_{j}$ is the contribution from the BSM
signal to reco bin $j$ (of both signal regions combined), and $\mu$ is a constant that represents the overall BSM signal strength.
Instead of being estimated in MC, \nZg[j,all] is a freely floating fit parameter (one for each reco \ETgamma\ bin $j$).
The total reconstructed event yield \nl\ in each single-$\ell$ control region ($\ell \in \{e,\mu\}$) is estimated according to
\begin{equation}
  \nl[,j] = \frac{\fZW[,j]\nZg[j,all]}{\RWl[,j]} + b_{\ell\Pgamma,j}.
\end{equation}
The total reconstructed event yield \nll\ in each double-$\ell$ control region is similarly estimated according to
\begin{equation}
  \nll[,j] = \frac{\nZg[j,all]}{\RZll[,j]} + b_{\ell\ell\Pgamma,j}.
\end{equation}
where $b_{\ell\ell\Pgamma,j}$ is the estimated contribution from processes other than \zllg\ in the double-$\ell$ control region.
The complete likelihood function is
\begin{align}
  \mathcal{L} & = \left\{ \mathcal{L_{\text{Signal}}} \mathcal{L_{\text{Control}}} \right\} \times \mathcal{L_{\text{Nuisances}}} \\
  & = \prod_{j} \left\{
    \prod_{S=H,V} \mathcal{P}\left( N_{S, j} \left| \nS[,j] (\vec{\theta} \right.) \right)
     \prod_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \nl[,j] (\vec{\theta}) \right. \right)
      \prod_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\ell\Pgamma, j} \left| \nll[,j] (\vec{\theta}) \right. \right) 
    \right\}  \times \prod_{t} \mathcal{N}(\theta_t) \\
  & = \prod_{j} \left\{
  \begin{array}{cc}
    \prod\limits_{S=H,V} \mathcal{P}\left( N_{S, j} \left| C_{S} \left(\mu s_{j}(\vec{\theta}) + (1 + \fZW[,j])\nZg[j,all](\vec{\theta}) + b_{j}(\vec{\theta})\right) + h \nhalo[,j](\vec{\theta}) \right. \right) \\[1.3pt]
    \times \prod\limits_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \frac{\fZW[,j]\nZg[j,all]}{\RWl[,j](\vec{\theta})} + b_{\ell\Pgamma, j}(\vec{\theta}) \right. \right) \\[1.3pt]
    \times \prod\limits_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\ell\Pgamma, j} \left| \frac{\nZg[j,all]}{\RZll[,j](\vec{\theta})} + b_{\ell\ell\Pgamma, j}(\vec{\theta}) \right. \right) \\[1.3pt]
  \end{array} \right\}
  \times \prod_{t} \mathcal{N}(\theta_t).
\end{align}

>>>>

\chapter{Signal and background estimation} \label{chap:background_estimation}
\section{Yields from simulation} \label{sec:background_estimation_simulated}
If a well-validated MC sample exists for a given process (Chap.~\ref{chap:simulation}), and if appropriate data--MC correction factors are applied (Chap.~\ref{chap:event_selection}),
the expected event yield contributed by that process to a given signal or control region may be estimated entirely within simulation.
After generating some large number of events (sufficient to render statistical uncertainties negligible with respect to other sources of uncertainty),
running them through the detector simulation, and reconstructing the results, the appropriate signal or control region cuts are finally applied to the simulated events.
The number of events passing all cuts, divided by the total number of events generated, gives a maximum-likelihood (ML) estimate of the probability that
an event of the kind modeled by the sample will contribute to the final observed event tally. This probability is often written as the product of two factors: the
probability that an event lies within the kinematic coverage of the detector, and the probability that an event within the kinematic coverage passes selection cuts,
called the \textit{acceptance} ($A$) and \textit{efficiency} ($\epsilon$), respectively. The expected contribution of a given process to a final event tally is therefore given by
\begin{equation}
\mathrm{expected\ yield} = A*\epsilon*\sigma*L
\end{equation}
where $\sigma$ is the total cross section of a given process (having kinematic properties within the range modeled by the MC sample) and $L$ is the integrated
luminosity of the observed dataset (35.9\fbinv).

\section{Electron background} \label{sec:background_estimation_elefake}
An inclusive estimate of the electron faking photon yield, summed over all processes with an isolated final-state electron, is obtained using a \textit{fake ratio} method.
The ratio of the numbers of successful vs. unsuccessful fakes is evaluated in a dedicated control region, designed in such a way that this ratio is expected to be equally
valid in the signal regions. Multiplying this ratio by the observed number of unsuccessful fake events in the signal regions gives an estimate of the number of successful
fake events in the signal regions. This last step in particular distinguishes the fake ratio method from e.g. finding a data--MC correction factor and applying that to
a purely MC-derived estimate of electron fake yields. Since the final expected yield is proportional to a set of observed (as opposed to simulated) data,
this is known as a \textit{data-driven} method.

@@

\section{Jet background} \label{sec:background_estimation_jetfake}
Like the electron faking photon background, the expected jet faking photon background is estimated via a data-driven method employing a fake ratio.
The numerator of the fake ratio should be the number of fake photon events originating from jets (passing any given signal or control region definition), and so
is defined by selecting events with a leading photon passing our standard photon ID.
The denominator should the number of events in which a high-\ET\ reconstructed photon is surrounded by so much energy from other particles
that it fails a loose set of isolation criteria (and so the photon is likely a jet constituent rather than a true hard-process photon); it is defined by selecting events
with a photon failing a relatively loose ID that has a 90\% selection efficiency for real photons\footnote{Denominator events must still pass a
``very loose'' ID with five times higher maximum isolation cuts.}.

@@

\section{Spike background} \label{sec:background_estimation_spikes}
Due to their idiosyncratic means of production, spikes (sec.~\ref{sec:LHCCMS_CMS_ECAL}) do not currently have simulated samples that could be expected to accurately reproduce their expected yield,
particularly in the case of events somehow passing all the spike cleaning cuts in the monophoton signal regions. Instead, the time distribution of clearly-identified
spikes in observed events can be used to extrapolate the preponderance of spikes within the in-time window ($|t|<3\unit{ns}$) defined by our signal region cuts.
This time distribution is examined by performing a custom reconstruction of the data in which ``spike-killer'' cuts that are part of standard event reconstruction (sec.~\ref{sec:reconstruction_egamma})
are omitted. Spike candidates are selected from reconstructed photons that pass a loosened set of ID criteria with no isolation cuts (to account for the different
characteristics of events outside the in-time window) but have $\ETgamma > 175\unit{GeV}$, $\sieie < 0.0104$, and either \sieie\ or $\sipip < 0.1$.
As illustrated in Fig.~\ref{fig:fulltime_templates}, this distribution exhibits a peak around $t = -15\unit{ns}$ and falls off to near zero by the in-time window.

@@

\begin{table}[tbp]
  \begin{center}
    \label{tab:response_matrix_values}
    \begin{tabular}{c c c c c c}
      \hline
       0.297401 & 0.0428149 & 0.000595967 & 5.87982e-05 & 0 & 0 \\
       0.0399934 & 0.38611 & 0.049973 & 0.000505446 & 0.000133614 & 0 \\
       0.000202488 & 0.0214437 & 0.37027 & 0.0326231 & 0.000264926 & 0.000183209 \\
       0 & 0.000196144 & 0.0229108 & 0.367465 & 0.0249473 & 0 \\
       0 & 0 & 1.50756e-05 & 0.0100609 & 0.343767 & 0.022748 \\
       0 & 0 & 0 & 0 & 0.00326465 & 0.316482 \\
      \hline
    \end{tabular}
    \caption{
      The values of the response matrix $K$, estimated in \zinvg\ MadGraph MC with higher order corrections applied.
      With rows ordered from top to bottom and columns ordered from left to right, the value in row $i$, column $j$
      is equal to the conditional probability of a \zinvg\ event to pass all signal region cuts and land in reconstructed
      \ETgamma\ bin $j$, if its true \pTgamma\ value is in bin $i$.
    }
  \end{center}
\end{table}

Measuring the \zinvg\ differential cross section amounts to extracting the true number of \zinvg\ events in each bin of \pTgamma, and
dividing by the integrated luminosity of our dataset. We denote the total numbers of events expected in each of our six reconstructed
\ETgamma\ bins by a vector $N$, and the expected background (anything other than \zinvg) by a vector $b$. The numbers
of produced \zinvg\ events, represented by $\lambda$, are related to $N$ and $b$ by the expected response matrix $K$ according to
\begin{equation}
  N = K \lambda + b
\end{equation}
The problem of extracting the differential \zinvg\ cross section from the observed \ETgamma\ distribution---unfolding---is then essentially a problem
of matrix inversion, in which we want to find
\begin{equation}
  \lambda = K^{-1} (N - b)
\end{equation}

@@

% Because $K$ is strongly diagonal and has similar values all along its diagonal, its inversion is not expected to result in any mathematical pathologies.
% The condition number of the matrix, defined to be the ratio of its largest to its smallest singular value, is 1.5363. It is invertible, and
% its inversion produces positive estimates of the cross section in every \ETgamma\ bin. There is no clear motivation to employ any sort of regularization
% strategy in the ML fit, and we do not employ any such strategy.

@@

\begin{table}
  \begin{center}
    \label{tab:zg_kfactors}
    \begin{tabular}{| l | r | r |}
      \hline
      \pTgamma\ [GeV] & \zinvg & \wlng \\
      \hline
      \hline
      $[175, 190]$ & 1.44 & 1.40 \\
      \hline
      $[190, 250]$ & 1.41 & 1.37 \\
      \hline
      $[250, 400]$ & 1.35 & 1.31 \\
      \hline
      $[400, 700]$ & 1.29 & 1.26 \\
      \hline
      $[700, \inf]$ & 1.15 & 1.15 \\
      \hline
    \end{tabular}
    \caption{NNLO / LO correction factors for \zinvg\ and \wlng\ samples.}
  \end{center}
\end{table}

@@

The differential cross section after all higher-order corrections are applied may be written as
\begin{equation}
  d\sigma^{\mathrm{NNLO\ QCD}+\mathrm{NLO\ EWK}} = d\sigma^{\mathrm{LO}} k^{\mathrm{NNLO\ QCD}} (1 + \kappa^{\mathrm{EWK\ Sudakov}} + \kappa^{\mathrm{EWK\ \Pq\Pgamma}})
\end{equation}
where $k^{\mathrm{NNLO\ QCD}} = d\sigma^{\mathrm{NNLO\ QCD}} / d\sigma^{\mathrm{LO}}$, and the two $\kappa$
terms are the Sudakov suppression and photon-induced enhancement components of the EWK
correction, respectively. Theoretical uncertainties on the EWK corrections are not currently well-understood. In this thesis,
the magnitudes of the uncertainties on $\kappa^{\mathrm{EWK\ Sudakov}}$ and $\kappa^{\mathrm{EWK\ \Pq\Pgamma}}$ are estimated
to be $(\kappa^{\mathrm{EWK\ Sudakov}})^2$ and $\kappa^{\mathrm{EWK\ \Pq\Pgamma}}$, i.e. the square of
the correction and 100\% of the correction, respectively\footnote{Choosing the square of $\kappa^{\mathrm{EWK\ Sudakov}}$ is motivated by the fact
that fully resummed leading-log Sudakov suppression is an exponential function of $\kappa^{\mathrm{EWK\ Sudakov}}$.}.

@@

\section{Signal estimation: SM} \label{sec:signal_extraction_SM}
Beam halo is the only process examined in this analysis with an anisotropic $\phi$ distribution.
Figure~\ref{fig:halophi} shows the distribution of beam halo photons as a function of $\phi'$ (defined in eq.~\ref{eq:phiprime}).
To constrain the beam halo normalization, the signal region is split into two parts according to $|\phi'|$.
The parts defined by $|\phi'| < 0.5$ and $|\phi'| > 0.5$ are respectively called the horizontal ($H$) and vertical ($V$) signal
regions. All other sources of events have expected yields that are isotropic in $\phi$, and therefore
are expected to fall into the two signal regions in direct proportion to the $\phi$ coverage of those regions.
The fraction of the total $\phi$ span covered by signal region $S$ is denoted by $C_{S}$ ($S \in \{H,V\}$).

@@

Using the above definitions for $C_{S}$, $r_{i}$, $\nZg[j,i]$, $h$, and $\nhalo[,j]$,
the total reconstructed event yield \nS\ in each signal region is estimated according to
\begin{equation}
  \nS[,j] = C_{S} (\Sigma_{i}r_{i}\nZg[j,i] + \nWg[j] + b_{j}) + h\nhalo[,j]
\end{equation}
where $\nWg[j]$ is the total contribution of \wlng\ events to reco bin $j$, and $b_{j}$ is the total contribution to reco bin $j$ from
electron and hadron misidentification, ECAL spikes, and other minor SM background processes, in both signal regions combined.

The ratios (\textit{transfer factors}) of the bin-by-bin yields of \wlng\ in the signal regions to those
of \wlng\ in the single-lepton control regions are denoted by \RWl[,j]. These are estimated in MC.
The total reconstructed event yield \nl\ in each single-$\ell$ control region ($\ell \in \{e,\mu\}$) is estimated according to
\begin{equation}
  \nl[,j] = \frac{\nWg[j]}{\RWl[,j]} + b_{\ell\Pgamma,j}
\end{equation}
where \nWg\ is the number of \wlng\ events in the combined signal regions, and
$b_{\ell\Pgamma}$ is the predicted contribution from other background sources in the single-$l$ control region.
Figure~\ref{fig:tf_w} shows the transfer factors relating the \wlng\ yield in the single-lepton control regions to the \wlng\ yield in the
vertical signal region.

@@

The complete likelihood function that is maximized in the SM cross section fit is
\begin{align}
\begin{split}
  \mathcal{L} & = \left\{ \mathcal{L_{\text{Signal}}} \mathcal{L_{\text{Control}}} \right\} \times \mathcal{L_{\text{Nuisances}}} \\
  & = \prod_{j} \left\{
    \prod_{S=H,V} \mathcal{P}\left( N_{S, j} \left| \nS[,j] (\vec{\theta} \right.) \right) \prod_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \nl[,j] (\vec{\theta}) \right. \right) 
    \right\}  \times \prod_{t} \mathcal{N}(\theta_t) \\
  & = \prod_{j} \left\{
  \begin{array}{cc}
    \prod\limits_{S=H,V} \mathcal{P}\left( N_{S, j} \left| C_{S} \left(\Sigma_{i}r_{i}\nZg[j,i](\vec{\theta}) + \nWg[j] + b_{j}(\vec{\theta})\right) + h \nhalo[,j](\vec{\theta}) \right. \right) \\[1.3pt]
    \times \prod\limits_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \frac{\nWg[j]}{\RWl[,j](\vec{\theta})} + b_{\ell\Pgamma, j}(\vec{\theta}) \right. \right) \\[1.3pt]
  \end{array} \right\}
  \times \prod_{t} \mathcal{N}(\theta_t)
\end{split}
\end{align}
following the notation introduced above, and where $\mathcal{P}(N\vert\lambda)$ is the Poisson probability of $N$ for mean $\lambda$,
$\mathcal{N}$ denotes the unit normal distribution centered at zero, and $N_{X,i}$ is the observed number of events in reco bin i of region X.

@@

The total reconstructed event yield \nS\ in each signal region is estimated according to
\begin{equation}
  \nS[,j] = C_{S} (\mu s_{j} + (1 + \fZW[,j])\nZg[j,all] + b_{j}) + h\nhalo[,j]
\end{equation}
where $\nZg[j,all]$ refers to the total contribution from all \zinvg\ events to reco \ETgamma\ bin $j$, $s_{j}$ is the contribution from the BSM
signal to reco bin $j$ (of both signal regions combined), and $\mu$ is a constant that represents the overall BSM signal strength.
Instead of being estimated in MC, \nZg[j,all] is a freely floating fit parameter (one for each reco \ETgamma\ bin $j$).
The total reconstructed event yield \nl\ in each single-$\ell$ control region ($\ell \in \{e,\mu\}$) is estimated according to
\begin{equation}
  \nl[,j] = \frac{\fZW[,j]\nZg[j,all]}{\RWl[,j]} + b_{\ell\Pgamma,j}
\end{equation}
The total reconstructed event yield \nll\ in each double-$\ell$ control region is similarly estimated according to
\begin{equation}
  \nll[,j] = \frac{\nZg[j,all]}{\RZll[,j]} + b_{\ell\ell\Pgamma,j}
\end{equation}
where $b_{\ell\ell\Pgamma,j}$ is the estimated contribution from processes other than \zllg\ in the double-$\ell$ control region.
The complete likelihood function is
\begin{align}
\begin{split}
  \mathcal{L} & = \left\{ \mathcal{L_{\text{Signal}}} \mathcal{L_{\text{Control}}} \right\} \times \mathcal{L_{\text{Nuisances}}} \\
  & = \prod_{j} \left\{
    \prod_{S=H,V} \mathcal{P}\left( N_{S, j} \left| \nS[,j] (\vec{\theta} \right.) \right)
     \prod_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \nl[,j] (\vec{\theta}) \right. \right)
      \prod_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\ell\Pgamma, j} \left| \nll[,j] (\vec{\theta}) \right. \right) 
    \right\}  \times \prod_{t} \mathcal{N}(\theta_t) \\
  & = \prod_{j} \left\{
  \begin{array}{cc}
    \prod\limits_{S=H,V} \mathcal{P}\left( N_{S, j} \left| C_{S} \left(\mu s_{j}(\vec{\theta}) + (1 + \fZW[,j])\nZg[j,all](\vec{\theta}) + b_{j}(\vec{\theta})\right) + h \nhalo[,j](\vec{\theta}) \right. \right) \\[1.3pt]
    \times \prod\limits_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\Pgamma, j} \left| \frac{\fZW[,j]\nZg[j,all]}{\RWl[,j](\vec{\theta})} + b_{\ell\Pgamma, j}(\vec{\theta}) \right. \right) \\[1.3pt]
    \times \prod\limits_{\ell=\Pe,\Pmu} \mathcal{P}\left( N_{\ell\ell\Pgamma, j} \left| \frac{\nZg[j,all]}{\RZll[,j](\vec{\theta})} + b_{\ell\ell\Pgamma, j}(\vec{\theta}) \right. \right) \\[1.3pt]
  \end{array} \right\}
  \times \prod_{t} \mathcal{N}(\theta_t)
\end{split}
\end{align}
